---
title: "European energy"
date: 2020-08-08
output: html_output
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)

theme_set(theme_light())

```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2020-08-04")

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}

energy_types_tidy <- tt$energy_types %>% 
  pivot_longer(
    cols = `2016`:`2018`,
    names_to = "year",
    values_to = "energy_gwh"
  )


# print
energy_types_tidy %>% 
  count(type)

```


# Visualise

Let's first take a look at a barplot representing energy rates and proportions over time
```{r}
energy_types_tidy %>% 
  count(type, year, wt = energy_gwh, name = "tot_energy_gwh") %>% 
  mutate(
    across(
      .cols = type, 
      .fns = ~ ..1 %>% 
        fct_reorder(desc(tot_energy_gwh)) %>% 
        fct_lump_n(n = 5, w = tot_energy_gwh)
    )
  ) %>% 
  ggplot(.) +
  aes(x = year, y = tot_energy_gwh, fill = type) +
  geom_col() +
  scale_y_continuous(
    labels = scales::comma_format(scale = 1e-6, suffix = "m", accuracy = 0.1),
    expand = expansion(mult = c(0, 0.05))
  ) +
  labs(
    x = NULL,
    y = "Total energy usage (GWh)",
    title = "Total energy usage by year and type of energy production",
    subtitle = "Conventional thermal remains dominant"
  )
```



\
what about a bar chart with the highest energy producing nations?
```{r}
energy_types_tidy %>% 
  filter(year == 2018) %>% 
  count(country, type, wt = energy_gwh, name = "tot_energy_gwh") %>% 
  mutate(
    across(
      .cols = country,
      .fns = ~ ..1 %>% 
        fct_reorder(.x = tot_energy_gwh, .fun = sum) %>% 
        fct_lump_n(n = 20, w = tot_energy_gwh)
    ),
    across(
      .cols = type,
      .fns = ~ ..1 %>% 
        fct_reorder(.x = tot_energy_gwh, .fun = sum)
    )
  ) %>% 
  filter(country != "Other") %>% 
  ggplot(.) +
  aes(x = tot_energy_gwh, y = country, fill = type) +
  geom_col() +
  scale_x_continuous(
    labels = scales::comma_format(scale = 1e-3, suffix = "k", accuracy = 0.1),
    expand = expansion(mult = c(0, 0.05))
  ) +
  labs(
    x = "Total Energy GWH"
  )
  
```




```{r}
energy_types_tidy %>% 
  filter(year == 2018) %>% 
  count(country_name, type, wt = energy_gwh) %>% 
  filter(!is.na(country_name)) %>% 
  mutate(
    across(
      .cols = country_name,
      .fns = ~ ..1 %>% 
        fct_lump_n(n = 20, w = n) %>% 
        fct_reorder(.x = n, .fun = sum)
    ),
    across(
      .cols = type,
      .fns = ~ ..1 %>% 
        fct_reorder(.x = n, .fun = sum)
    )
  ) %>% 
  filter(country_name != "Other") %>% 
  ggplot(.) +
  aes(x = n, y = country_name, fill = type) +
  geom_col(position = "fill") +
  scale_x_continuous(
    labels = scales::percent_format(),
    expand = expansion(mult = c(0,0))
  ) +
  scale_fill_viridis_d(option = "inferno") +
  labs(
    x = "Percentage of energy usage by production type",
    y = NULL,
    title = "Proportion of energy use by country and type of energy production",
    subtitle = "Norway or the hydro-way!!~"
  ) +
  theme(
    legend.position = "bottom"
  )
```

